 


\section{Q1}
\label{part1}
\begin{enumerate}


\item For the text you saved for the 10000 URIs from A1, Q2:
- Use the “boilerpipe” software to remove the HTML templates from all HTML pages (document how many pages link from the tweets were non-HTML and had to be skipped)
- \url{https://code.google.com/p/boilerpipe/}
- WSDM 2010 paper: \url{http://www.l3s.de/~kohlschuetter/boilerplate/}

\item For how many of the 10000 URIs was boilerpipe successful?
- Compare the total words, unique words, and byte sizes before and after use of boilerpipe

\item For what classes of pages was it successful?

\item For what classes of pages was it unsuccessful?

\item Provide examples of both successful and unsuccessful removals and discuss at length.

\end{enumerate}

\subsection{Solution}

\begin{enumerate}

\item I already had the HTML documents downloaded for the 10,000 URIs from A1, Q2.
\item I wrote a python program using boilerpipe library to fetch just the text from the 10,000 URIs.
\item At this point, I had two collections of documents which is stated above.
\item Out of 10000 URIs, boilerpipe worked for 5661 URIs.
\item It returned 404 for 1818 URIs and 2521 URIs had no content in the generated files.
\item It was successful in the cases where the webpage contain only HTML and no scripting embedded in it whereas it failed when some kind of scripting was present in the HTML page.

\item Examples of successful URIs: \newline \newline
- \url{https://amp.twimg.com/v/24d799c3-48ba-4695-a2bb-9bafb4afc412} \newline
- \url{http://www.mirror.co.uk/news/uk-news/coalition-minister-centre-abuse-claims-5094966} \newline
- \url{http://exclaim.ca/Music/article/punch_brothers-phosphorescent_blues}	

\item Examples of unsuccessful URIs: \newline \newline
- \url{http://maneking.jp/index.html?ic=gn_twp_ltm2&af=75sf2xw12344558844} \newline
- \url{http://dorogobuzh.f-z-l.ru/dieta-babkinoy-nadezhdi-pevitsi-i-ee-menyu.php59} \newline
- \url{http://www.dunyabulteni.net/haberler/321299/sudanda-iki-rus-pilot-kacirildi?utm_source=dlvr.it&utm_medium=twitter62}
	
\item Observation on the number of words and byte size of both the document collections is that - the number of total words, unique words and byte size after boilerpipe is way too less as compared to the document collection which has HTML documents for all the URIs. The exact numbers are presented below.


\end{enumerate}

\newpage

\subsection{Summary: Before boilerpipe/ HTML documents}

\begingroup
\obeylines
\input{before-boilerpipe-summary.txt}
\endgroup

\subsection{Summary: After boilerpipe/ Text from the webpages}
\begingroup
\obeylines
\input{after-boilerpipe-summary.txt}
\endgroup

\subsection{Code Listing}
\subsubsection{fetchWebpages.py}

\lstinputlisting[language=Python,breaklines = true,frame=single,caption={Python program to fetch HTML documents for the 10,000 URIs of A1, Q2}, label=lst:q1-1,captionpos=b,numbers=left,showspaces=false,showstringspaces=false,basicstyle=\footnotesize]{fetchWebpages.py}
\newpage

\subsubsection{extractTextWithBoilerpipe.py}
\lstinputlisting[language=Python,breaklines = true,frame=single,caption={Python program to fetch only text for the same URIs as above}, label=lst:q1-1,captionpos=b,numbers=left,showspaces=false,showstringspaces=false,basicstyle=\footnotesize]{extractTextWithBoilerpipe.py}
\newpage














